---
title: "Exploratory Data Analysis"
output: html_notebook
date: 2020-05-12
---

```{r setup, include=FALSE}
source("code/packages.R")

knitr::opts_chunk$set(
  echo = TRUE,
  fig.width = 6,
  fig.asp = 0.618,
  out.width = "70%",
  fig.align = "center",
  fig.show = "hold",
  eval = TRUE
)

loadd(
  raw_us_data,
  us_data,
  pop_density_data,
  state_level_data,
  rt_data,
  rf_model_list
)
```

# Examining the *unprocessed* Google mobility data for the United States

Missing value counts for each variable.
```{r raw-us-missing-values}
raw_us_data %>%
  map(~ sum(is.na(.x)))
```

Unique country codes in the data. Only the United States, as expected.
```{r raw-us-unique-country-codes}
raw_us_data %>%
  pull(country_region) %>%
  unique()
```

All the states represented in the data. Note that "NA" denotes national-level
data.
```{r raw-us-data-states}
raw_us_data %>%
  pull(sub_region_1) %>%
  unique()
```

Counts of each county (and other second-level sub-regions) represented in the
data.
```{r raw-us-data-sub-region-counts}
raw_us_data %>%
  count(sub_region_1, sub_region_2)
```

Date ranges included in the data for each state.
```{r raw-us-data-date-ranges}
raw_us_data %>%
  group_by(sub_region_1) %>%
  summarize(
    min = min(date),
    max = max(date)
  )
```

# Examining the *processed* Google mobility data for the United States

State codes included in the data. Note that "US" denotes national-level data and
"DC" denotes the District of Columbia.
```{r us-data-states}
us_data %>%
  pull(sub_region_1) %>%
  unique()
```

# Examining the state-level data

Missing value counts for each variable.
```{r state-level-missing-values}
state_level_data %>%
  map(~ sum(is.na(.x)))
```

<!-- TODO: For some reason GitHub markdown doesn't like equation mode. -->
# Examining the R_t data

State codes included in the data.
```{r rt-states}
rt_data %>%
  pull(region) %>%
  unique()
```

Total number of regions included in the data. We have all 50 states plus DC.
```{r rt-states-count}
rt_data %>%
  pull(region) %>%
  n_distinct()
```

# Density by region

Density by region (all 50 states plus DC). Data from the 2010 United States
Census.
```{r density-by-region, fig.width=8}
ggplot(pop_density_data, aes(region, density)) +
  geom_point() +
  geom_segment(aes(x = region, y = 0, xend = region, yend = density)) +
  theme(axis.text.x = element_text(angle = 90, size = 8, vjust = 0.5))
```

# Examining the model data

<!-- TODO -->

# Examining the random forest models

Just the raw variable importance measures for now. Random forest models were fit
to the data after lagging the explanatory variables by 0, 1, ..., 14 days. In
each case below we just look at the model with the the lowest MSE when fit to
the data.

## Plain model (run on entire data set)

Lag that gave lowest MSE.
```{r rf-plain-model-best-lag}
model_list <- rf_model_list$plain
mse_scores <- model_list %>% map(~ .x$mse)
which.min(mse_scores) - 1
```

```{r rf-plain-model-importance}
best_model <- model_list[[which.min(mse_scores)]]$model
importance(best_model)
```

```{r rf-plain-model-importance-plot, fig.width=8}
varImpPlot(best_model)
```

## Model excluding DC

Lag that gave lowest MSE.
```{r rf-no_dc-model-best-lag}
model_list <- rf_model_list$no_dc
mse_scores <- model_list %>% map(~ .x$mse)
which.min(mse_scores) - 1
```

```{r rf-no_dc-model-importance}
best_model <- model_list[[which.min(mse_scores)]]$model
importance(best_model)
```

```{r rf-no_dc-model-importance-plot, fig.width=8}
varImpPlot(best_model)
```

## Model excluding NY

Lag that gave lowest MSE.
```{r rf-no_ny-model-best-lag}
model_list <- rf_model_list$no_ny
mse_scores <- model_list %>% map(~ .x$mse)
which.min(mse_scores) - 1
```

```{r rf-no_ny-model-importance}
best_model <- model_list[[which.min(mse_scores)]]$model
importance(best_model)
```

```{r rf-no_ny-model-importance-plot, fig.width=8}
varImpPlot(best_model)
```

## Model excluding highest density states (CT, DC, MA, MD, NJ, and RI)

Lag that gave lowest MSE.
```{r rf-low_density-model-best-lag}
model_list <- rf_model_list$low_density
mse_scores <- model_list %>% map(~ .x$mse)
which.min(mse_scores) - 1
```

```{r rf-low_density-model-importance}
best_model <- model_list[[which.min(mse_scores)]]$model
importance(best_model)
```

```{r rf-low_density-model-importance-plot, fig.width=8}
varImpPlot(best_model)
```

# Session info

```{r session-info}
sessionInfo()
```
