---
title: "Random forest models -- without regions, with lockdown indicator"
output: html_notebook
date: 2020-05-13
---

```{r setup, include=FALSE}
source("code/packages.R")

knitr::opts_chunk$set(
  echo = TRUE,
  fig.width = 6,
  fig.asp = 0.618,
  out.width = "70%",
  fig.align = "center",
  fig.show = "hold",
  eval = TRUE
)

loadd(rf_model2_list)
rf_model_list <- rf_model2_list
```

# Random forest models -- without regions, with lockdown indicator

Just the raw variable importance measures for now. Random forest models were fit
to the data after lagging the explanatory variables by 0, 1, ..., 14 days. In
each case below we just look at the model with the the lowest MSE when fit to
the data.

## Plain model (run on entire data set)

Lag that gave lowest MSE.
```{r rf-plain-model-best-lag}
model_list <- rf_model_list$plain
mse_scores <- model_list %>% map(~ .x$mse)
which.min(mse_scores) - 1
```

```{r rf-plain-model-importance}
best_model <- model_list[[which.min(mse_scores)]]$model
importance(best_model)
```

```{r rf-plain-model-importance-plot, fig.width=8}
varImpPlot(best_model)
```

## Model excluding DC

Lag that gave lowest MSE.
```{r rf-no_dc-model-best-lag}
model_list <- rf_model_list$no_dc
mse_scores <- model_list %>% map(~ .x$mse)
which.min(mse_scores) - 1
```

```{r rf-no_dc-model-importance}
best_model <- model_list[[which.min(mse_scores)]]$model
importance(best_model)
```

```{r rf-no_dc-model-importance-plot, fig.width=8}
varImpPlot(best_model)
```

## Model excluding NY

Lag that gave lowest MSE.
```{r rf-no_ny-model-best-lag}
model_list <- rf_model_list$no_ny
mse_scores <- model_list %>% map(~ .x$mse)
which.min(mse_scores) - 1
```

```{r rf-no_ny-model-importance}
best_model <- model_list[[which.min(mse_scores)]]$model
importance(best_model)
```

```{r rf-no_ny-model-importance-plot, fig.width=8}
varImpPlot(best_model)
```

## Model excluding highest density states (CT, DC, MA, MD, NJ, and RI)

Lag that gave lowest MSE.
```{r rf-low_density-model-best-lag}
model_list <- rf_model_list$low_density
mse_scores <- model_list %>% map(~ .x$mse)
which.min(mse_scores) - 1
```

```{r rf-low_density-model-importance}
best_model <- model_list[[which.min(mse_scores)]]$model
importance(best_model)
```

```{r rf-low_density-model-importance-plot, fig.width=8}
varImpPlot(best_model)
```
